### 2015-06-11 WhitePapers/revise_chunks/paper-body.tex
Update chunk index paper results
Former-commit-id: 56f2835ea9cecbc020dd71e179bab084f45883b2

With these data structures in place, when the chunked dataset is on disk and
has only one unlimited maximum dimension, the extensible array indexing method is used,
allowing chunk access in $O(1)$ time. When it has more than one unlimited
maximum dimension sizes, the B-tree version 2 indexing method is used, allowing
chunk access in $O(\log_b{n})$, with $b$ the order of the tree and $n$ the
number of nodes. When it is in cache, the chunk is accessed through the cache
hash table and the computed hash value .

@@

\begin{table}
\centering
\caption{Result for all three test settings after optimization.}
\label{tab:result2}
\begin{tabular}{lr} \toprule
Indexing Method &
Time (\si{\second}) \\
\midrule
\textit{Along the X-direction} \\
EA & $27.54$\tikzmark{x1}\\
BT1 & $34.01$\tikzmark{x2} \\
BT2 & $31.59$\tikzmark{x3} \\
\midrule
\textit{Along the Y-direction} \\
EA & $29.24$\tikzmark{y1} \\
BT1 & $42.97$\tikzmark{y2} \\
BT2 & $33.72$\tikzmark{y3} \\
\midrule
\textit{Along the XY-direction} \\
EA & $-$ \\
BT1 & $35.46$\tikzmark{xy1} \\
BT2 & $32.92$\tikzmark{xy2} \\
\bottomrule
\end{tabular}
\tablearrowright{x2}{x1}{$\simeq -19\%$}{}
\tablearrowleft{x2}{x3}{$\simeq -7\%$}{fill=paperblue!30}
\tablearrowright{y2}{y1}{$\simeq -32\%$}{}
\tablearrowleft{y2}{y3}{$\simeq -22\%$}{fill=paperblue!30}
\tablearrowleft{xy1}{xy2}{$\simeq -7\%$}{fill=paperblue!30}
\end{table}

>>>>

With these data structures in place, when the chunked dataset is on disk and
has only one unlimited maximum dimension, the extensible array indexing method is used,
allowing chunk access in $O(1)$ time. When it has more than one unlimited
maximum dimension sizes, the B-tree version 2 indexing method is used, allowing
chunk access in $O(\log_b{n})$, with $b$ the order of the tree and $n$ the
number of nodes. When it is in cache, the chunk is accessed through the cache
hash table and the computed hash value.

@@

\begin{table}
\centering
\caption{Result for all three test settings after optimization.}
\label{tab:result2}
\begin{tabular}{lr} \toprule
Indexing Method &
Time (\si{\second}) \\
\midrule
\textit{Along the X-direction} \\
EA & $32.10$\tikzmark{x1}\\
BT1 & $36.63$\tikzmark{x2} \\
BT2 & $35.39$\tikzmark{x3} \\
\midrule
\textit{Along the Y-direction} \\
EA & $32.2$\tikzmark{y1} \\
BT1 & $39.01$\tikzmark{y2} \\
BT2 & $34.90$\tikzmark{y3} \\
\midrule
\textit{Along the XY-direction} \\
EA & $-$ \\
BT1 & $36.11$\tikzmark{xy1} \\
BT2 & $35.29$\tikzmark{xy2} \\
\bottomrule
\end{tabular}
\tablearrowright{x2}{x1}{$\simeq -12.4\%$}{}
\tablearrowleft{x2}{x3}{$\simeq -3.4\%$}{fill=paperblue!30}
\tablearrowright{y2}{y1}{$\simeq -17.5\%$}{}
\tablearrowleft{y2}{y3}{$\simeq -10.5\%$}{fill=paperblue!30}
\tablearrowleft{xy1}{xy2}{$\simeq -2.3\%$}{fill=paperblue!30}
\end{table}
